---
title: "Sales Prediction Carseats"
author: "Lana Korošec"
date: "2023-08-09"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Dataset Carseats frpm ISLR package is a study case of sales prediction.

We will forecast sales based on variables: 
price, 
advertising, 
ShelveLoc (3-factor variable - positioning quality)

Regarding given data, we change factos in variable ShelveLoc to have "natural" order from "bad to good"

```{r, include=FALSE, warning=FALSE}
library(ggplot2)
library(gridExtra)
library(ISLR)
library(effects)
library(car)
library(multcomp)

Carseats$ShelveLoc <- factor(Carseats$ShelveLoc, levels=c("Bad","Medium", "Good"))

```



## Data presentation

```{r, echo=FALSE, warning=FALSE}


#data(Carseats)
#dim(Carseats)
summary(Carseats)

ggplot(data = Carseats, aes(x=Price, y=Sales, color = ShelveLoc))+
  geom_point()+
ggtitle(label = "Sales/Price")+
  geom_smooth(method = "lm", se = FALSE) 



ggplot(data = Carseats, aes(x=Advertising, y=Sales, color = ShelveLoc))+
  geom_point()+
ggtitle(label = "Sales/Advertising")+
  geom_smooth(method = "lm", se = FALSE) 

```

The influence of ShelveLoc, that is shelve location, is clear from both graph. Whereas we see that Price in comparison with Advertising has greater impact on sales.

These are first impressions, but lets dive in the research itself.

## Analysis

First, we would like to see if there is interaction between pairs of predictor variables:
- ShelveLoc and Price
- ShelveLoc and Advertising


```{r, echo=FALSE, warning=FALSE}

p1 <- ggplot(data = Carseats, aes(x = Price, y = Sales)) +
  facet_grid(.~ShelveLoc) + geom_point() +
  xlab("Price (USD)")  +   ylab("Sales (1000)")+
  geom_smooth(se=FALSE)
p2 <- ggplot(data = Carseats, aes(x = Advertising, y = Sales)) +
  facet_grid(.~ShelveLoc) +  geom_point() +
  xlab("Advertising (1000 USD)")  +   ylab("Sales (1000)")+
  geom_smooth(se=FALSE)


grid.arrange(p1, p2, nrow = 2, ncol = 1)


```


Using smoother we discover that it might be reasonable to take into account interaction between advertising and shelveLoc when creating linear model. 

Further we use statistical test to get correct answer. 

We create one model without interaction and one model with interaction and check ANOVA. It turns out the interaction is unsignificant.


```{r, echo=FALSE}

model.seat = lm(Sales~Price+Advertising+ShelveLoc, data = Carseats)

summary(model.seat)

model.seatInt = lm(Sales~Price+Advertising+ShelveLoc+Price:ShelveLoc+Advertising:ShelveLoc, data = Carseats)

summary(model.seatInt)

anova(model.seat, model.seatInt) #H0 je da se ne razlikujeta


```

Therefore we continue with model.seat.

At this point we check whether there is interaction between Price and Advertising

```{r, echo=FALSE}


plot(Effect(c("Advertising", "Price", "ShelveLoc"), model.seat,
            partial.residuals = TRUE), ci.style = "none")

model.seatInt2 = lm(Sales~Price*Advertising+ShelveLoc, data = Carseats)

plot(Effect(c("Advertising", "Price", "ShelveLoc"), model.seatInt2,
            partial.residuals = TRUE), ci.style = "none")


anova(model.seat, model.seatInt2) #tisto kar smo videli na "Effects" je zanemarljiva

```

We see that interaction between numeric predictors is as well insignificant.


## Model diagnosis model.seat

```{r, echo=FALSE}

summary(model.seat)
par(mfrow = c(2, 2),  oma = c(0, 0, 2, 0))
plot(model.seat)

confint(model.seat)


#model.seat$coefficients

```

The coefficient of determination R2 has a value of 0.609.

The model explains 60.9 % of variability of Sales. 

The expected Sales is 10.54. 1 m/s increase in wind speed results in almost 8.5 hundreths decrease in 110 metres hurdles run result.



```{r, echo=FALSE}
avPlots(model.seat)
```

Price has the most significant impact on Sales, which represents the slope of the line. 


```{r, echo=FALSE}
crPlots(model.seat) #ce ni interakcije, ce bi bila moramo effect
#gladilniki se dobro prilegajo, vse štima - šolsko je model O.K.

anova(model.seat)

```

## Results

For "official results" to make sure that confidence intervals are correct, though we are testing multiple hypothesis, we use correction with the use of multcomp glth

```{r, echo=FALSE}

#results = glht(model.seat)
#summary(results)
#confint(results)


plot(Effect(c("Price", "ShelveLoc"), model.seat), main="",
     multiline=TRUE, ci.style="bands", ylim=c(0, 17))


plot(Effect(c("Advertising", "ShelveLoc"), model.seat), main="",
     multiline=TRUE, ci.style="bands", ylim=c(0, 17))

```

The upper graphics represents results assuming an average value of advertising.


```{r, echo=FALSE}

results = glht(model.seat)
summary(results)
confint(results)


plot(Effect(c("Advertising", "ShelveLoc"), model.seat), main="",
     multiline=TRUE, ci.style="bands", ylim=c(0, 17))

```

The upper graphics represents results assuming an average price (reduction).


## Remark

The case study was done and has been presented in the course Linear Models by Damjana Kastelec UNI LJ 22/23
